systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-23 paper/trunk/systemfit_intro.tex
added section about the code inside the systemfit package (this is suggested by the JSS)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@617 591db2bd-e0a0-4d22-8c19-2192dbb7da31
two modifications in the introduction and in the summary due to the inclusion of section "testing reliability" (in the previous revision)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@622 591db2bd-e0a0-4d22-8c19-2192dbb7da31
corrected a grammar mistake in the introduction
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@625 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Many theoretical models that are econometrically estimated
consist of more than one equation.
In this case, the disturbance terms of these equations are likely
to be contemporaneously correlated,
because some unconsidered factors
that influence the disturbance term in one equation
probably influence the disturbance terms in other equations
of these model, too.
Ignoring this contemporaneous correlation
and estimating these equations separately
leads to inefficient parameter estimates.
However, estimating all equations simultaneously,
taking the covariance structure of the residuals into account,
leads to efficient estimates.
This estimation procedure is generally called
°Seemingly Unrelated Regression° (SUR) \citep{zellner62}.
Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions.%
\footnote{
Especially the economic theory suggests many cross-equation parameter
restrictions (e.g.\ the symmetry restriction in demand models).
}
These restrictions can be tested and/or imposed only in a simultaneous
estimation approach.

@@

This paper is organized as follows:
In the following Section~\ref{sec:statistics} we
introduce the statistical background of estimating equation systems.
Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit} and especially how the features presented in the previous
section can be used.
Finally, a summary and outlook are presented in
Section~\ref{sec:Summmary}.

>>>>

Many theoretical models that are econometrically estimated
consist of more than one equation.
In this case, the disturbance terms of these equations are likely
to be contemporaneously correlated,
because some unconsidered factors
that influence the disturbance term in one equation
probably influence the disturbance terms in other equations
of this model, too.
Ignoring this contemporaneous correlation
and estimating these equations separately
leads to inefficient parameter estimates.
However, estimating all equations simultaneously,
taking the covariance structure of the residuals into account,
leads to efficient estimates.
This estimation procedure is generally called
°Seemingly Unrelated Regression° (SUR) \citep{zellner62}.
Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions.%
\footnote{
Especially the economic theory suggests many cross-equation parameter
restrictions (e.g.\ the symmetry restriction in demand models).
}
These restrictions can be tested and/or imposed only in a simultaneous
estimation approach.

@@

This paper is organized as follows:
In the following Section~\ref{sec:statistics} we
introduce the statistical background of estimating equation systems.
The implementation of the statistical procedures in \proglang{R}
is shortly explained in Section~\ref{sec:code}.
Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit} and especially how the features presented in the previous
section can be used.
In Section~\ref{sec:reliability} the reliability of the results from
\pkg{systemfit} are tested.
Finally, a summary and outlook are presented in
Section~\ref{sec:Summmary}.
